A Comparative study of Dask and Spark for neuroimaging pipelines

### 2019-07-02 latex/paper.tex
some changes in intro

\section{Introduction}
% Context
With the increasing number of data available in neuroimaging,~\cite{ALFAROALMAGRO:18,
UKBioBank:18} the processing of Big Data becomes critical. Frameworks like
Nipype~\cite{Nipype:11} are usually used to create neuroimaging pipelines however it
is worth considering the use of general purpose Big Data
frameworks~\cite{Hayot-Sasson:17}. In that research, Spark~\cite{Spark:16} was a
natural choice as it is the state-of-the-art framework for Big Data. Since our
laboratory mostly works with Python, we want to know if Dask~\cite{Dask:15}, a Python
written framework, could bring better or similar performances while facilitating
usage.

>>>>

\section{Introduction}
% Context
\VHS{it's not the the processing of BD becomes critical, it's that the results obtained
from processing more data should be more reliable\dots and the data is there too}
The recent rise in data sharing and improved data collection strategies
have brought neuroimaging to the Big Data era ~\cite{ALFAROALMAGRO:18,
UKBioBank:18}. Existing neuroimaging frameworks, such as Nipype~\cite{Nipype:11},
are well suited for processing the standard compute-intensive neuroimaging pipelines,
but lack incorporation Big Data strategies (i.e. in-memory computing,
data locality and lazy-evaluation) to improve performance of the increasingly
prevalent data-intensive pipelines. As was noted in ~\cite{Hayot-Sasson:17}, 
in-memory computing, coupled with data locality, can bring significant performance
improvements to data intensive neuroimaging pipelines. We extend this work by studying
the differences between two Big Data frameworks, Dask~\cite{Dask:15} and Apache Spark~\cite{Spark:16},
for their suitability in the processing neuroimaging pipelines.
